Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-03-15 analyses/scripts/full_data_extraction_citation_table.Rmd
removed explicit namespacing and turned off long table format

```{r}
#columns 2-5 with paper titles
knitr::kable(final_citation_table %>% 
                 dplyr::select(1:5), 
             format = "latex", booktabs = TRUE, 
             longtable = TRUE#,
             #caption = 'Extracted data per paper: publication_year, author_affiliation_type, country_studied, author_in_country_studied.'
             ) %>% 
    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
    kableExtra::column_spec(column = c(1, 3), width = "5cm") %>% 
    kableExtra::landscape()
```

```{r}
#columns 6-10 with paper titles
knitr::kable(final_citation_table %>% 
                 dplyr::select(1, 6:10), 
             format = "latex", booktabs = TRUE, 
             longtable = TRUE#,
             #caption = 'Extracted data per paper: disease, objectives, individual_representation, space_representation, model_structure.'
             ) %>% 
    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
    kableExtra::column_spec(column = c(1), width = "5cm") %>% 
    kableExtra::landscape()
```

```{r}
#columns 11-15 with paper titles
knitr::kable(final_citation_table %>% 
                 dplyr::select(1, 11:15), 
             format = "latex", booktabs = TRUE, 
             longtable = TRUE#,
           #  caption = 'Extracted data per paper: parametrization, validation, outbreak_type, intervention_modelled, vax_modelled_with_non_vax.'
             ) %>% 
    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
    kableExtra::column_spec(column = c(1, 2, 5), width = "4cm") %>% 
    kableExtra::landscape()
```

```{r}
#columns 16-22 with paper titles
knitr::kable(final_citation_table %>% 
                 dplyr::select(1, 16:22), 
             format = "latex", booktabs = TRUE, 
             longtable = TRUE#,
           #  caption = 'Extracted data per paper: is_vax_effective, outcome_measured, sensitivity_analysis, data_used, data_available, simulation_code_available, vax_modelled.'
             ) %>% 
    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
    kableExtra::column_spec(column = c(1, 3), width = "5cm") %>% 
    kableExtra::landscape()
```

>>>>

```{r}
#columns 2-5 with paper titles
kable(final_citation_table %>% 
                 dplyr::select(1:5), 
             format = "latex", 
             booktabs = TRUE, 
             longtable = FALSE#,
             #caption = 'Extracted data per paper: publication_year, author_affiliation_type, country_studied, author_in_country_studied.'
             ) %>% 
    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
    column_spec(column = c(1, 3), width = "5cm") %>%
    landscape()
```

```{r}
#columns 6-10 with paper titles
kable(final_citation_table %>% 
                 dplyr::select(1, 6:10), 
             format = "latex", booktabs = TRUE, 
             longtable = FALSE#,
             #caption = 'Extracted data per paper: disease, objectives, individual_representation, space_representation, model_structure.'
             ) %>% 
    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
    column_spec(column = c(1), width = "5cm") %>% 
    landscape()
```

```{r}
#columns 11-15 with paper titles
kable(final_citation_table %>% 
                 dplyr::select(1, 11:15), 
             format = "latex", booktabs = TRUE, 
             longtable = FALSE#,
           #  caption = 'Extracted data per paper: parametrization, validation, outbreak_type, intervention_modelled, vax_modelled_with_non_vax.'
             ) %>% 
    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
    column_spec(column = c(1, 2, 5), width = "4cm") %>% 
    landscape()
```

```{r}
#columns 16-22 with paper titles
kable(final_citation_table %>% 
                 dplyr::select(1, 16:22), 
             format = "latex", booktabs = TRUE, 
             longtable = FALSE#,
           #  caption = 'Extracted data per paper: is_vax_effective, outcome_measured, sensitivity_analysis, data_used, data_available, simulation_code_available, vax_modelled.'
             ) %>% 
    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
    column_spec(column = c(1, 3), width = "5cm") %>% 
    landscape()
```
